### 2021-10-29 SujetStage/2021-pNetsubjectM2.tex
une petite passe pour preciser les choses

In the previous years, we have studied theoretical foundations for open
systems and we defined  open automata \cite{arxiv-weakbisim,henrio:Forte2016,hou:hal-02406098} that can be seen as labelled transition systems (LTSs) with parameters and holes. The transitions of open
automata are much more complex than transitions of an LTS: they include guards expressing the relations between the parameters of the automaton with the actions of the holes, and assignments encoding their effects.
% as the firing on a transition depends on parameters and actions that are symbolic.
Holes here are modeling the environment of the open automaton, that can be used to compose open automata together to build bigger systems. We proved that our models 
have good properties, namely that composition preserves some classes of equivalences.

The composition of open automata refers to filling holes, it requires to check the compatibility of their sorts. Nowadays, we simply say that two open automata are compatible if they consist of the same actions with the same arity. But, 
 we are interested in enriching holes with description of behaviours to give them enough power and enable us to check equivalences for these open systems. The description will characterise all the
interactions and the series of inputs and outputs of data exchanged between the automata and its surroundings. Precisely, the theory of session types and behavioural types  \cite{Fantechi:MLTCDP2019} are intended  to describe dynamic aspects of the behaviour of processes.

>>>>

In the previous years, we have studied theoretical foundations for open
systems and we defined  open automata \cite{arxiv-weakbisim,henrio:Forte2016,hou:hal-02406098} that can be seen as labelled transition systems (LTSs) with parameters and holes. The transitions of open
automata are much more complex than transitions of an LTS: they include guards expressing the relations between the parameters of the automaton with the actions of the holes, and assignments encoding their effects.
% as the firing on a transition depends on parameters and actions that are symbolic.
 We proved that our models 
have good properties, namely that composition preserves some properties like bisimulation.

The composition of open automata refers to filling holes, it requires to check the compatibility of their sorts. Nowadays, we simply verify the compatibility of two automata to be composed based on   action labels and  arity. But, 
 we are interested in enriching holes with description of behaviours to give them enough power and enable us to check equivalences for these open systems. The description will characterise all the
interactions and the series of inputs and outputs of data exchanged between the automata and its surroundings. Precisely, the theory of session types and behavioural types  \cite{Fantechi:MLTCDP2019} are intended  to describe dynamic aspects of the behaviour of processes.
